\documentclass[a4paper]{article}
\usepackage[margin=2cm]{geometry}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{array}
\graphicspath{ {/} }
\author{Ayush Agarwal}
\begin{document}
\section*{\huge\textbf Ayush Agarwal}
\hrule
\section*{}
\begin{minipage}{.45\linewidth}
\begin{flushleft}
 Third year Undergraduate,\\
 Computer Science and Engineering,\\
 IIT Kanpur.
 \end{flushleft}
 \end{minipage}
 \hfill
 \begin{minipage}{.45\linewidth}
 \begin{flushright}
 B-223/10, IIT Kanpur\\
 $8090686935$\\
 $ayushaga@iitk.ac.in$\\
 \end{flushright}
 \end{minipage}
 %%%%%%%%%%%%%%---Education---%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Education}
 \hrule
 \begin{center}
 \vspace{2mm}
  \begin{tabular}{|c|c|c|c|}
  \hline
  Year & Degree & Institute & CPI\\
  \hline
  2017(Expected)& B.Tech, Computer Sc.&IIT Kanpur&$8.5/10$\\
  \hline
  2013& HSCE&St.Anselm's Sr. Sec. School&89\% \\
  \hline
  2011& AISSE&St.Anselm's Sr. Sec. School&10/10 \\
  \hline
  \end{tabular}
 \end{center} 
  
%%%%%%%%%%%%%%%%%%--Achievements----%%%%%%%%%%%%%%%%%%%
 \section*{Achievements}
 \hrule
 \vspace{2mm}
  \begin{itemize}
   \itemsep-0.3em
   \item All India Rank \textbf{146} in \textbf{JEE}-Advance, 2013.	
   \item \textbf{NTSE} and KVPY \textbf{Scholar} 
   \item Bronze in \textbf{Inter-IIT}(2015) Data Analytics competetion.
   \item Rank-\textbf{1} in International Mathematics Olympiad(IMO) by SOF.
   \item Among final \textbf{35} students selected for \textbf{OCSC} Camp for International Physics Olympiad(\textbf{IPhO}),2013 .
   \item Cleared Regional Mathematics Olympiad(\textbf{RMO}) and National Standard Examination in Astronomy(\textbf{NSEA}).
   \item Secured AIR-\textbf{8} in stage-1 National Science Olympiad(\textbf{NSO}) by SOF.
  \end{itemize}
 
 
%%%%%%%%%%%%%%%%----Projects---%%%%%%%%%%%%
\section*{Projects}
\hrule
\vspace{2mm}
  \begin{itemize}
  \item
   \textbf{Backend Development and Network Establishment}
  \begin{itemize}
          \textit{under Prof. Manindra Agarwal}
      \item Developed the backend \textbf{Models} and \textbf{Api} in \textbf{Scala} using the \textbf{Akka} framework
          for handling http requests, \textbf{Argonaut} for marshalling/unmarshalling of json,
          and \textbf{Slick} for dealing with \textbf{PostgresSQL} database.\\
          Developed a Cookie based \textbf{Stateless} Authentication System.\\
          Established a cross host overlay network among \textbf{Dockers} in a \textbf{CoreOS}
           cluster using \textbf{Weave}.
    \end{itemize}
   \item 
    \textbf{Hotel Recommendation System}
	   \begin{itemize}
	    \item Developed a hotel recommendation based on the customer reviews.
            Wrote python scripts using \textbf{BeautifulSoup} to crawl customer review data from tripadvisor.
            Used this data for \textbf{LDA} to assign rankings to the hotels.
	   \end{itemize}
    \item
    \textbf{Portal for Academic Mentor System for Counselling Service,IITK}
	   \begin{itemize}
	    \item Developed an online portal for better interaction of Counselling 
            Service and academically deficient students. Used \textbf{MVC} architecture 
            from a \textbf{Codeignitor} (php-framework).
	   \end{itemize}
  \end{itemize}

  %%%%%%%%%%%%%%-------Courses-----------------%%%%%%%%%%%%
\section*{Relevant Courses}
\hrule
\vspace{1mm}
\begin{flushright}(*)Ongoing Courses\\
\end{flushright}
%%%\vspace{1mm}
\begin{minipage}{.45\linewidth}
      \begin{flushleft}                           
          \begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} l}
              \textbf{ESC101} & Introduction to Prog.\\
              \textbf{CS210}  & Data Structure and Algorithms\\
              \textbf{CS220}  & Computer Organisation\\
              \textbf{CS251}  & Computing Lab-I\\
              \textbf{CS345*} & Algorithms - II\\
                
            \end{tabular*}
      \end{flushleft} 
  \end{minipage}
  \hfill
  \begin{minipage}{.5\linewidth}
      \begin{flushright}                                      
          \begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} l}
              \textbf{MSO201}  & Probability and Statistics\\
              \textbf{CS330*}  & Operating Systems \\
              \textbf{CS252*}  & Computing Lab-II\\
              \textbf{CS340*}  & Theory of Computation\\
              \textbf{CS653*}  & Functional Programming in Haskell\\
            \end{tabular*}
      \end{flushright} 
  \end{minipage}
  
 %%%%%%%%%%%%%%%%--------Technical Skills--------%%%%%%%%%%%%%
 \section*{Technical Skills}
 \hrule
 \vspace{2mm}
  \begin{tabular}{@{}m{4.0cm}m{13cm}@{}}
   \textbf{\textrm{Languages}} & 
Scala, C, C$++$, Python, Php, Dart, Bash Scripting, Verilog\\ 
  \textbf{\textrm{Platforms}} &
  Linux, CoreOS, Windows\\
  
  \textbf{\textrm{Tools}} &
  Akka, PostgresSQL, Angular, docker, weave, vagrant, Git, Sbt, Octave\\
  \end{tabular}



\end{document}

