\documentclass[a4paper]{article}
\usepackage[margin=2cm]{geometry}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{array}
\graphicspath{ {/} }
\author{Ayush Agarwal}
\begin{document}
\section*{\huge\textbf Ayush Agarwal}
\begin{minipage}{.45\linewidth}
\begin{flushleft}
 Third year Undergraduate,\\
 Computer Science and Engineering,\\
 IIT Kanpur.
 \end{flushleft}
 \end{minipage}
 \hfill
 \begin{minipage}{.45\linewidth}
 \begin{flushright}
 G-115/9, IIT Kanpur\\
 $8090686935$\\
 $agarwal.ayush9@gmail.com$\\
 \end{flushright}
 \end{minipage}
 %%%%%%%%%%%%%%---Education---%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Education}
 \hrule
 \begin{center}
 \vspace{3mm}
  \begin{tabular}{|c|c|c|c|}
  \hline
  Year & Degree & Institute & CPI\\
  \hline
  2017(Expected)& B.Tech, Computer Sc.&IIT Kanpur&$8.6/10$\\
  \hline
  2013& HSCE&St.Anselm's Sr. Sec. School&89\% \\
  \hline
  2011& AISSE&St.Anselm's Sr. Sec. School&10/10 \\
  \hline
  \end{tabular}
 \end{center} 
  
%%%%%%%%%%%%%%%%%%--Achievements----%%%%%%%%%%%%%%%%%%%
 \section*{Achievements}
 \hrule
 \vspace{3mm}
  \begin{itemize}
   \setlength\itemsep{-0.2em}
   \item All India Rank \textbf{146} in \textbf{JEE}-Advanced 2013 given by 0.15 million students.
   \item \textbf{HackCon 2015}, \textbf{Runners up} in the nation wide \textbf{CTF} organised by IIIT-D.
   \item \textbf{Build The Shield}, Finished 10th in the nation wide \textbf{CTF} organised by \textbf{Microsoft}.
   \item \textbf{NTSE} and KVPY \textbf{Scholar} 
   \item Bronze in \textbf{Inter-IIT}(2015) Data Analytics competetion.
   \item Rank-\textbf{1} in International Mathematics Olympiad(IMO) by SOF.
   \item Among final \textbf{35} students selected for \textbf{OCSC} Camp for International Physics Olympiad(\textbf{IPhO}),2013.
   \item Cleared Regional Mathematics Olympiad(\textbf{RMO}) and National Standard Examination in Astronomy(\textbf{NSEA}).
   \item Secured AIR-\textbf{8} in stage-1 National Science Olympiad(\textbf{NSO}) by SOF.
  \end{itemize}
 
 
%%%%%%%%%%%%%%%%----Projects---%%%%%%%%%%%%
\section*{Internships}
\hrule
\vspace{3mm}
  \begin{itemize}
  \item
    \textbf{Cache Side-Channeling Attacks}
         \hfill \textit{under Prof. Brendan Dolan-Gavitt, NYU Tandon, 2016}
      \begin{itemize}
      \setlength\itemsep{-0.2em}
          \item Studied different forms of possible Cache Side Channel attacks.
          \item Implemented the side channel attack to exploit the AES key from OpenSSL implementation.
          \item Proposed and implemented a simple, lightweight and generalised binary search based defense mechanism to detect any known cache-side channel attacks.
      \end{itemize}
  \item
   \textbf{Online Management Portal}
         \hfill \textit{under Prof. Manindra Agarwal, 2015}
  \begin{itemize}
      \setlength\itemsep{-0.2em}
      \item Developed the backend \textbf{Models} and \textbf{Api} in \textbf{Scala} using the \textbf{Akka's actor model} on top of a minimal framework.
       \item Developed a Cookie based \textbf{Stateless} Authentication System.
       \item Established a cross host overlay network among \textbf{Dockers} in a \textbf{CoreOS}
           cluster using \textbf{Weave}.
       \item Designed and developed the frontend using bleeding edge frameworks like AngularDart, Polymer, etc.
  \end{itemize}
  \end{itemize}

\section*{Projects}
\hrule
\vspace{2mm}
  \begin{itemize}
     \setlength\itemsep{-0.1em}
     \item
    \textbf{CROC}
    \hfill \textit{under Prof. Purshottam Kar, 2016}
      \begin{itemize}
      \setlength\itemsep{-0.2em}
      \item Extensively studied state of the art SVMs and cutting plane techniques for multi-label classification.
      \item Explored various performance measures like Precision@k, Area Under Curve (AUC), partial AUC (pAUC) and their existing algorithms to gain insight into the existing optimisation techniques for such performance measures
      \item Proposed a novel algorithm for optimising Concentrated ROC (CROC) and partial CROC (pCROC), performance measures
originating from the field of Bioinformatics for optimising early retrieval
      \item Presently running experiments on offline and online learning using the proposed algorithm and aiming for a publication
      \end{itemize}

\vspace{6mm}

    \item 
    \textbf{HScraper}
    \hfill \textit{under Prof. Piyush Kurur, 2015}
    
	\begin{itemize}
      \setlength\itemsep{-0.2em}
      \item Designed and developed a web crawling and parsing library in \textbf{haskell} as part of CS653 project.
        \item HTML parser was developed on top of Parsec. Library also has support for parsing malformed HTML using html-tidy.
        \item Provides functionalities similar to BeautifulSoup of python.
    \end{itemize}



  \item
    \textbf{Scala Compiler}
    \hfill \textit{under Prof. Subhajit Roy, 2016}
	\begin{itemize}
      \setlength\itemsep{-0.2em}
      \item Programmed a Scala to x86 cross compiler with support for basic datatypes, conditional statements, looping statements,
arrays, nested functions and recursion.
      \item Hosted on https://github.com/agarwalayush/scalaCompiler\\
    \end{itemize}

  \item
    \textbf{NachOS}
    \hfill \textit{under Prof. Mainak Chaudhari, 2015}
      \begin{itemize}
      \setlength\itemsep{-0.2em}
        \item Implemented system calls pertaining to Fork, Exec, Join, Yield, Sleep and Exit for NachOS (a rudimentary OS).
        \item Programmed different signal handling methods, process scheduling and page replacement algorithms and evaluated
their relative performance.
      \end{itemize}

  \item
    \textbf{Object Detection and Classification in Traffic Surveillance Video}
      \begin{itemize}
      \setlength\itemsep{-0.2em}
        \item Extracted regions of interest from the video using image processing algorithms.
        \item Experimented with different feature representations of images like HoG and SIFT for training the classifiers
        \item Achieved a classification accuracy of 88.8\%  using Linear SVC as classifier and HoG feature representation.
      \end{itemize}



  \item
    \textbf{Hotel Recommendation System}
    \hfill \textit{2014}
	   \begin{itemize}
      \setlength\itemsep{-0.2em}
	    \item Developed a hotel recommendation based on the customer reviews.
        \item Wrote python scripts using \textbf{BeautifulSoup} to crawl customer review data from tripadvisor.
        \item Used this data for \textbf{LDA} to assign rankings to the hotels.
	   \end{itemize}
    \item
\vspace{3mm}
    \textbf{Portal for Academic Mentor System for Counselling Service,IITK}
    \hfill \textit{2014}
	   \begin{itemize}
	    \item Developed an online portal for better interaction of Counselling 
            Service and academically deficient students. Used \textbf{MVC} architecture 
            from a \textbf{Codeignitor} (php-framework).
	   \end{itemize}
      \end{itemize}

  %%%%%%%%%%%%%%-------Courses-----------------%%%%%%%%%%%%
\section*{Relevant Courses}
\hrule
\vspace{2mm}
\vspace{1mm}
\begin{minipage}{.45\linewidth}
      \begin{flushleft}                           
          \begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} l}
              Computer System Security\\
              Compiler Design\\
              Computer Organisation\\
              Algorithms - II\\
              Data Structure and Algorithms\\
              Computer Networks
            \end{tabular*}
      \end{flushleft} 
  \end{minipage}
  \hfill
  \begin{minipage}{.5\linewidth}
      \begin{flushright}                                      
          \begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} l}
              Advanced Operating Systems\\
              Operating Systems \\
              Functional Programming \\
              Theory of Computation\\
              Introduction to Databases\\
              Machine Learning\\
            \end{tabular*}
      \end{flushright} 
  \end{minipage}
  
 %%%%%%%%%%%%%%%%--------Technical Skills--------%%%%%%%%%%%%%
 \section*{Technical Skills}
 \hrule
 \vspace{3mm}
  \begin{tabular}{@{}m{4.0cm}m{13cm}@{}}
   \textbf{\textrm{Languages}} & 
Haskell, Scala, C, C$++$, Python, Php, Dart, JavaScript, Bash Scripting\\ 
  \textbf{\textrm{Platforms}} &
Linux (Arch Linux, Ubuntu, CoreOS), Windows\\
  
  \textbf{\textrm{Tools}} &
  PostgresSQL, Node.js, Angular, docker, weave, vagrant\\
  & Z3, Git, Sbt\\
  \end{tabular}

 %%%%%%%%%%%%%%%%--------Extras--------%%%%%%%%%%%%%


\end{document}

